---
title: "Programa de Prevención y Control del Dengue de Veracruz"
output: 
  flexdashboard::flex_dashboard:
      theme: united
      social: ["twitter", "facebook", "menu", "github"]
output_dir: libs      
---

```{r setup}

# Step 1. load the library ####
options(shiny.maxRequestSize=30*1024^2)
library(formattable)
library(tmap)
library(rmarkdown)
library(knitr)
library(shiny)
library(flexdashboard)
library(plotly)
library(boldenr)
library(magrittr)
library(leaflet)
library(ggplot2)
library(dplyr)
library(stringr)
library(dash)
library(ECharts2Shiny)
library(sf)

# Step 3. load the functions ####
if(as.vector(Sys.info()["sysname"]) == "Darwin"){
    
    # 1.6 hotspots cases
    source("~/Dropbox/r_developments/r_new_functions/3.Functions/risk_agebs.R")
    
    source("~/Dropbox/r_developments/r_new_functions/3.Functions/risk_map.R")
    
    source("~/Dropbox/r_developments/r_new_functions/3.Functions/hotspots_map.R")
    
    # 1. 7 eggs hotspots ####
    
    source("~/Dropbox/r_developments/r_dashboards/github_pages/test_denv_dash_oax/3.Functions/eggs_hotspots_intensity_map_year.R")

    
} else if(as.vector(Sys.info()["sysname"]) == "Windows"){
    # 1.1. dengue dataset
    
    # 1.5 ulv dataset
    
    # 1.6 hotspots


    #Step  load the risk_ageb function ###
    source('C:/Users/HOME/Dropbox/r_developments/r_dashboards/github_pages/test_dashboard/3.Functions/risk_agebs.R')

    # Step  load the risk_map function ####
    source("D:/OneDrive/proyects/hotspots/3.Functions/risk_map.R")

    # Step  load the hotspots map ####
    source("C:/Users/HOME/Dropbox/r_developments/r_dashboards/github_pages/test_dashboard/3.Functions/hotspots_map.R")
    
    # 1. 7 eggs hotspots ####
    source("C:/Users/HOME/Dropbox/r_developments/r_dashboards/github_pages/test_denv_dash_oax/3.Functions/eggs_hotspots_intensity_map_year.R")
    
} else if(as.vector(Sys.info()["sysname"]) == "Linux"){
    
}



# Step 5. Load the RData files ####
if(as.vector(Sys.info()["sysname"]) == "Darwin"){
    # load the blocks
    load("~/OneDrive/automatic_read_ine_2010/8.RData/block_ine10_mx.RData")
    
    # load the dengue cases hotspots
    load("~/Dropbox/hotspots_2021/8.RData/cases_hotspots_agebs19.RData")
    hotspots <- cases_hotspots_agebs19 |>
    sf::st_make_valid()
    
    # load the vector hotspots
    load("~/OneDrive/proyects/hotspots_eggs/8.RData/31_yucatan/betas/31_yucatan_zinb1_betas.RData")
    
    
} else if(as.vector(Sys.info()["sysname"]) == "Windows"){
    
    # load the blocks #####
    load("D:/OneDrive/automatic_read_ine_2010/8.RData/block_ine10_mx.RData") 
    
    # Step 1. load the hotspots dengue cases ####
   load("E:/backup/Dropbox_respaldo_2023_01_03/hotspots_2022/8.RData/cases_hotspots_agebs19.RData")
    
    cases_hotspots_agebs19 <- cases_hotspots_agebs19 |>
    sf::st_make_valid()

    
    
    # load the vector hotspots
    load("D:/OneDrive/proyects/hotspots_eggs/8.RData/30_veracruz/betas/30_veracruz_zinb1_betas.RData")
    
} else if(as.vector(Sys.info()["sysname"]) == "Linux"){
    
}


```

# **Hotspots de la Transmisión de Dengue**

## Column {.tabset}

### [**Pánuco**]{style="color:#990000"}

```{r, hotspots_dengue_panuco, echo=FALSE}
hotspots_map(cve_ent = "30",
             locality = "Panuco",
             hotspots = cases_hotspots_agebs19,
             static_map = FALSE)

```


### [**Tuxpan**]{style="color:#990000"}

```{r, hotspots_dengue_tuxpan, echo=FALSE}
hotspots_map(cve_ent = "30",
             locality = "Tuxpan de Rodriguez Cano",
             hotspots = cases_hotspots_agebs19,
             static_map = FALSE)

```


### [**Poza Rica**]{style="color:#990000"}

```{r, hotspots_dengue_poza_rica, echo=FALSE}
hotspots_map(cve_ent = "30",
             locality = "Poza Rica de Hidalgo",
             hotspots = cases_hotspots_agebs19,
             static_map = FALSE)

```

### [**Papantla**]{style="color:#990000"}

```{r, hotspots_dengue_papantla, echo=FALSE}
hotspots_map(cve_ent = "30",
             locality = "Papantal de Olearte",
             hotspots = cases_hotspots_agebs19,
             static_map = FALSE)

```

### [**Martínez de la Torre**]{style="color:#990000"}

```{r, hotspots_dengue_martinez, echo=FALSE}
hotspots_map(cve_ent = "30",
             locality = "Martínez de la Torre",
             hotspots = cases_hotspots_agebs19,
             static_map = FALSE)

```


### [**Xalapa**]{style="color:#990000"}

```{r, hotspots_dengue_xalapa, echo=FALSE}
hotspots_map(cve_ent = "30",
             locality = "Xalapa-Enriquez",
             hotspots = cases_hotspots_agebs19,
             static_map = FALSE)

```


### [**Córdoba**]{style="color:#990000"}

```{r, hotspots_dengue_cordoba, echo=FALSE}
hotspots_map(cve_ent = "30",
             locality = "Cordoba",
             hotspots = cases_hotspots_agebs19,
             static_map = FALSE)

```

### [**Orizaba**]{style="color:#990000"}

```{r, hotspots_dengue_orizaba, echo=FALSE}
hotspots_map(cve_ent = "30",
             locality = "Orizaba",
             hotspots = cases_hotspots_agebs19,
             static_map = FALSE)

```


### [**Veracruz**]{style="color:#990000"}

```{r, hotspots_dengue_veracruz, echo=FALSE}
hotspots_map(cve_ent = "30",
             locality = c("Veracruz","Boca del Río"),
             hotspots = cases_hotspots_agebs19,
             static_map = FALSE)

```

### [**Cosamaloapan**]{style="color:#990000"}

```{r, hotspots_dengue_cosamaloapan, echo=FALSE}
hotspots_map(cve_ent = "30",
             locality = "Cosamaloapan",
             hotspots = cases_hotspots_agebs19,
             static_map = FALSE)

```

### [**San Andres Tuxtla**]{style="color:#990000"}

```{r, hotspots_dengue_san_andres, echo=FALSE}
hotspots_map(cve_ent = "30",
             locality = "San Andres Tuxtla",
             hotspots = cases_hotspots_agebs19,
             static_map = FALSE)

```


### [**Coatzacoalcos**]{style="color:#990000"}

```{r, hotspots_dengue_coatza, echo=FALSE}
hotspots_map(cve_ent = "30",
             locality = "Coatzacoalcos",
             hotspots = cases_hotspots_agebs19,
             static_map = FALSE)

```


### [**Minatitlan**]{style="color:#990000"}

```{r, hotspots_dengue_minatitlan, echo=FALSE}
hotspots_map(cve_ent = "30",
             locality = "Minatitlan",
             hotspots = cases_hotspots_agebs19,
             static_map = FALSE)

```

# **Hotspots del vector de Dengue**

## Column {.tabset}

### [**Tuxpan**]{style="color:#990000"}

```{r vector_hotspots_tuxpan, dpi = 300, warning=FALSE, message=FALSE}
eggs_hotspots_intensity_map_year(betas = betas_30_veracruz,
                                 locality = "Tuxpan de Rodríguez Cano",
                                 cve_ent = "30",
                                 palette = rcartocolor::carto_pal,
                                 name = "SunsetDark")
```
### [**Poza Rica**]{style="color:#990000"}

```{r vector_hotspots_poza_rica, dpi = 300, warning=FALSE, message=FALSE}
eggs_hotspots_intensity_map_year(betas = betas_30_veracruz,
                                 locality = "Poza Rica de Hidalgo",
                                 cve_ent = "30",
                                 palette = rcartocolor::carto_pal,
                                 name = "SunsetDark")
```

### [**Papantla**]{style="color:#990000"}

```{r vector_hotspots_papantla, dpi = 300, warning=FALSE, message=FALSE}
eggs_hotspots_intensity_map_year(betas = betas_30_veracruz,
                                 locality = "Papantla de Olearte",
                                 cve_ent = "30",
                                 palette = rcartocolor::carto_pal,
                                 name = "SunsetDark")
```



### [**Xalapa**]{style="color:#990000"}

```{r vector_hotspots_xalapa, dpi = 300, warning=FALSE, message=FALSE}
eggs_hotspots_intensity_map_year(betas = betas_30_veracruz,
                                 locality = "Xalapa-Enriquez",
                                 cve_ent = "30",
                                 palette = rcartocolor::carto_pal,
                                 name = "SunsetDark")
```

### [**Córdoba**]{style="color:#990000"}

```{r vector_hotspots_cordoba, dpi = 300, warning=FALSE, message=FALSE}
eggs_hotspots_intensity_map_year(betas = betas_30_veracruz,
                                 locality = "Cordoba",
                                 cve_ent = "30",
                                 palette = rcartocolor::carto_pal,
                                 name = "SunsetDark")
```

### [**Orizaba**]{style="color:#990000"}

```{r vector_hotspots_orizaba, dpi = 300, warning=FALSE, message=FALSE}
eggs_hotspots_intensity_map_year(betas = betas_30_veracruz,
                                 locality = "Orizaba",
                                 cve_ent = "30",
                                 palette = rcartocolor::carto_pal,
                                 name = "SunsetDark")
```


### [**Veracruz**]{style="color:#990000"}

```{r vector_hotspots_veracruz, dpi = 300, warning=FALSE, message=FALSE}
eggs_hotspots_intensity_map_year(betas = betas_30_veracruz,
                                 locality = "Veracruz",
                                 cve_ent = "30",
                                 palette = rcartocolor::carto_pal,
                                 name = "SunsetDark")
```


### [**Cosamaloapan**]{style="color:#990000"}

```{r vector_hotspots_cosamaloapan, dpi = 300, warning=FALSE, message=FALSE}
eggs_hotspots_intensity_map_year(betas = betas_30_veracruz,
                                 locality = "Tuxpan de Rodríguez Cano",
                                 cve_ent = "30",
                                 palette = rcartocolor::carto_pal,
                                 name = "SunsetDark")
```


### [**San Andres Tuxtla**]{style="color:#990000"}

```{r vector_hotspots_san_andres, dpi = 300, warning=FALSE, message=FALSE}
eggs_hotspots_intensity_map_year(betas = betas_30_veracruz,
                                 locality = "San Andres Tuxtla",
                                 cve_ent = "30",
                                 palette = rcartocolor::carto_pal,
                                 name = "SunsetDark")
```

### [**Coatzacoalcos**]{style="color:#990000"}

```{r vector_hotspots_coatza, dpi = 300, warning=FALSE, message=FALSE}
eggs_hotspots_intensity_map_year(betas = betas_30_veracruz,
                                 locality = "Coatzacoalcos",
                                 cve_ent = "30",
                                 palette = rcartocolor::carto_pal,
                                 name = "SunsetDark")
```


### [**Minatitlan**]{style="color:#990000"}

```{r vector_hotspots_minatitlan, dpi = 300, warning=FALSE, message=FALSE}
eggs_hotspots_intensity_map_year(betas = betas_30_veracruz,
                                 locality = "Minatitlan",
                                 cve_ent = "30",
                                 palette = rcartocolor::carto_pal,
                                 name = "SunsetDark")
```

# **Dengue Risk Maps**

## Column {.tabset}

### [**Panuco**]{style="color:#7d9029"}

```{r, risk_map_panuco, echo=FALSE}
risk <- risk_agebs(spde_model = betas_30_veracruz,
                          hotspots = cases_hotspots_agebs19,
                          locality = "Panuco",
                          cve_ent = "30",
                          intensity_perc = 25)
risk_map(risk = risk, staticmap = FALSE)
```
> Los hotspots del vector aun no estan actualizados

### [**Tuxpan**]{style="color:#7d9029"}

```{r, risk_map_tuxpan, echo=FALSE}
risk <- risk_agebs(spde_model = betas_30_veracruz,
                          hotspots = cases_hotspots_agebs19,
                          locality = "Tuxpan de Rodriguez Cano",
                          cve_ent = "30",
                          intensity_perc = 25)
risk_map(risk = risk, staticmap = FALSE)
```


### [**Poza Rica**]{style="color:#7d9029"}

```{r, risk_map_poza_rica, echo=FALSE}
risk <- risk_agebs(spde_model = betas_30_veracruz,
                          hotspots = cases_hotspots_agebs19,
                          locality = "Poza Rica de Hidalgo",
                          cve_ent = "30",
                          intensity_perc = 25)
risk_map(risk = risk, staticmap = FALSE)
```


### [**Papantla**]{style="color:#7d9029"}

```{r, risk_map_papantla, echo=FALSE}
risk <- risk_agebs(spde_model = betas_30_veracruz,
                          hotspots = cases_hotspots_agebs19,
                          locality = "Papantla de Olearte",
                          cve_ent = "30",
                          intensity_perc = 25)
risk_map(risk = risk, staticmap = FALSE)
```

### [**Martínez de la Torre**]{style="color:#7d9029"}

```{r, risk_map_martinez, echo=FALSE}
risk <- risk_agebs(spde_model = betas_30_veracruz,
                          hotspots = cases_hotspots_agebs19,
                          locality = "Martinez de la Torre",
                          cve_ent = "30",
                          intensity_perc = 25)
risk_map(risk = risk, staticmap = FALSE)
```
> Los hotspots del vector aun no estan actualizados

### [**Xalapa**]{style="color:#7d9029"}

```{r, risk_map_xalapa, echo=FALSE}
risk <- risk_agebs(spde_model = betas_30_veracruz,
                          hotspots = cases_hotspots_agebs19,
                          locality = "Xalapa-Enriquez",
                          cve_ent = "30",
                          intensity_perc = 25)
risk_map(risk = risk, staticmap = FALSE)
```


### [**Córdoba**]{style="color:#7d9029"}

```{r, risk_map_cordoba, echo=FALSE}
risk <- risk_agebs(spde_model = betas_30_veracruz,
                          hotspots = cases_hotspots_agebs19,
                          locality = "Cordoba",
                          cve_ent = "30",
                          intensity_perc = 25)
risk_map(risk = risk, staticmap = FALSE)
```


### [**Orizaba**]{style="color:#7d9029"}

```{r, risk_map_orizaba, echo=FALSE}
risk <- risk_agebs(spde_model = betas_30_veracruz,
                          hotspots = cases_hotspots_agebs19,
                          locality = "Orizaba",
                          cve_ent = "30",
                          intensity_perc = 25)
risk_map(risk = risk, staticmap = FALSE)
```



### [**Veracruz**]{style="color:#7d9029"}

```{r, risk_map_veracruz, echo=FALSE}
risk <- risk_agebs(spde_model = betas_30_veracruz,
                          hotspots = cases_hotspots_agebs19,
                          locality = "Veracruz",
                          cve_ent = "30",
                          intensity_perc = 25)
risk_map(risk = risk, staticmap = FALSE)
```



### [**Cosamaloapan**]{style="color:#7d9029"}

```{r, risk_map_cosamaloapan, echo=FALSE}
risk <- risk_agebs(spde_model = betas_30_veracruz,
                          hotspots = cases_hotspots_agebs19,
                          locality = "Cosamaloapan",
                          cve_ent = "30",
                          intensity_perc = 25)
risk_map(risk = risk, staticmap = FALSE)
```


### [**San Andres Tuxtla**]{style="color:#7d9029"}

```{r, risk_map_san_andres, echo=FALSE}
risk <- risk_agebs(spde_model = betas_30_veracruz,
                          hotspots = cases_hotspots_agebs19,
                          locality = "San Andres Tuxtla",
                          cve_ent = "30",
                          intensity_perc = 25)
risk_map(risk = risk, staticmap = FALSE)
```


### [**Coatzacoalcos**]{style="color:#7d9029"}

```{r, risk_map_coatzacoalcos, echo=FALSE}
risk <- risk_agebs(spde_model = betas_30_veracruz,
                          hotspots = cases_hotspots_agebs19,
                          locality = "Coatzacoalcos",
                          cve_ent = "30",
                          intensity_perc = 25)
risk_map(risk = risk, staticmap = FALSE)
```


### [**Minatitlan**]{style="color:#7d9029"}

```{r, risk_map_minatitlan, echo=FALSE}
risk <- risk_agebs(spde_model = betas_30_veracruz,
                          hotspots = cases_hotspots_agebs19,
                          locality = "Minatitlan",
                          cve_ent = "30",
                          intensity_perc = 25)
risk_map(risk = risk, staticmap = FALSE)
```
